%\VignetteIndexEntry{Introduction}
%\VignetteEngine{knitr}

```{r include = FALSE}
library(knitr)
opts_chunk$set(eval = FALSE)
```

# Introduction to arcpyr

The `arcpyr` package provides a simple interface to `arcpy` for R 
users. The interface should be straightforward to those who have
dabbled with Python and the `arcpy` module, or to those who have
done some basic work with ArcGIS Model Builder. If you don't fall
into either of those categories, don't worry! This vignette will 
show you the basics.

## Connecting to ArcGIS

The first step is to connect to ArcGIS. If you installed ArcGIS and 
Python to the default locations, `arcpyr` should be able to find what
it needs automatically. Otherwise, you might need to specify some 
folder locations. If you want to connect to ArcGIS Pro, make sure to
do `connect_ArcGIS(Pro = TRUE)`.

```{r}
library(arcpyr)
connect_ArcGIS()
```

## Creating the arcpy environment object

Once you have connected to ArcGIS, the next step is to create the arcpy
environment object. This object will contain all the ArcGIS tools you
want to access from R.

```{r}
arcpy = arcpy_env()
```

The code above creates an environment that contains all of the tools that are
accessible from you ArcGIS installation. In addition, it also creates an 
interface to the ArcGIS environment settings.

```{r}
ls(arcpy)         # list available tools
ls(arcpy$env)     # list available environment settings
```

Don't need all the tools? There are two ways to create a partial 
interface.

### Method 1: Specify the tools and settings you want

If you only need a few tools or environment settings, you can list them
in the call to `arcpy_env`.

```{r}
arcpy = arcpy_env(
  tool.list = c("Delete_managment", "Buffer_analysis"),
  env.list = c("workspace", "scratchWorkspace")
)
arcpy$Delete_managment("path/to/layer")
```

Note that if you're using tools from an ArcGIS extension, you'll need
to explicitly check out that extension via `checkout_extension()`.

### Method 2: Create an empty environment, and then add toolboxes

If you're going to be working extensively with only a few toolboxes,
you can create an empty arcpy environment and then add the toolboxes
individually.

```{r}
arcpy = arcpy_env(NULL) # Access all environment settings, but no tools
attach_toolbox(arcpy, "management")  # attach the management toolbox
attach_toolbox(arcpy, "statistics")  # attach the statistics toolbox
```

Adding toolboxes in this way will automatically check out any necessary 
extensions. Note that accessing the tools this way works a bit 
differently from the first method:

```{r}
arcpy$management$Delete("path/to/layer")
```

This may seem strange, but it's completely analogous to the different 
ways of accessing `arcpy` tools in Python:

```{python}
# method 1
import arcpy
arcpy.Delete_management('path/to/layer')

# method 2
import arcpy.management
arcpy.management.Delete('path/to/layer')
```

### Method 3 (not recommended): attach the environment

If you want to work with the `arcpy` tools directly in you environment,
you can use `attach`:

```{r}
attach(arcpy_env())
Delete_management('path/to/layer')
env$workspace()
```

Which is analagous to 

```{python}
from arcpy import *
Delete_management('path/to/layer')
env.workspace
```

in Python. Note that this can clutter your environment and lead to some naming 
conflicts, so I don't generally recommend it.

## Specify ArcGIS environment settings

Setting up the ArcGIS environment with `arcpyr` is only slightly 
different from Python. In `arcpyr`, environment settings are accessed 
via function calls.

```{r}
arcpy = arcpy_env()
arcpy$env$workspace()                     # get workspace location
arcpy$env$workspace("path/to/workspace")  # set workspace location
```

## Need more?

The `arcpyr` package focuses on providing an interface to ArcGIS 
toolboxes. It can't handle the object-oriented aspects of 
`arcpy` and Python, like doing raster calculations reading/writing 
attribute tables. If you need that sort of functionality, check out the 
`arcpyrextra` package. 
